Flatiron cleaning

### 2022-01-06 Rmd/rdi analysis.Rmd
Update rdi analysis

Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$

@@

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.

@@

study_criteria <- study_criteria %>%
  filter(!is.na(surgerydate))

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
```{r}
Frontline_adjusted <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**

@@

<!-- Patients left: -->
```{r}
Frontline_adjusted <- Frontline_adjusted %>%
  filter(is.na(switch_drugs))
```

@@

# **The final number of patients in the dataset is `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**

@@

### For Upfront Chemo
```{r}
data <- Frontline_adjusted %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

### For Upfront Surgery
```{r}
data <- Frontline_adjusted %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

# Frontline <- 
#   full_join(Frontline, imputed_data %>% 
#               select(patientid, starts_with("imp_")), 
#             by = "patientid") 
Frontline_adjusted <- 
  full_join(Frontline_adjusted, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```

@@

```{r consort}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("Assessed for eligibility") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

@@

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) &
              !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) &
              therapy == "Upfront Chemo") |
             (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
               therapy == "Upfront Surgery"))),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)),

  Frontline = standard_care %>% 
    filter(is.na(wrong_pacli_dosedense)),
  Frontline1 = Frontline %>%
    filter(is.na(switch_drugs))
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    flatiron_rec = "**flatiron_rec**",
    study_criteria = "*study_criteria*",
    missing_data = "missing_data",
    standard_care = "standard_care",
    Frontline = "Frontline",
    Frontline1 = "Population Study"
  )
study_cohorts

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 50, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "flatiron_rec", 5, 45, glue::glue(
      "{cohort_count_adorn(study_cohorts, flatiron_rec)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • Data from one PracticeID <br>
      • historical structured data were not available for <br> patients seen at academic sites prior to 2015
      ")

  ) %>%
  consort_box_add(
    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
  ) %>%
  consort_box_add(
    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%
  consort_box_add(
    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
  ) %>%

  consort_arrow_add(
    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
  ) %>%
  consort_arrow_add(
    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
  ) %>%
  consort_arrow_add(
    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
  ) %>%
  consort_arrow_add(
    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 18, margin_v = 1)
```

@@

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

@@

```{r}
Frontline <- Frontline_adjusted
```

@@

           "histology", "stagecat", imp_stagecat,

@@

<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
```{r Table 5}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat,
           "debulking", imp_debulking, "therapy"
           )) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

@@

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_drug >= 0.85              ~ "correct",
#     mean_RDI_per_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

@@

```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(y=raceeth, x=value,  fill=raceeth
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+

@@

Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(y=bmi_cat, x=value,  fill=bmi_cat
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+

@@

## 1.RDI summary table

@@

<span style="color:green">**Table 7: Summary RDI data by race and bmi**</span>  
Removing the overall on the right side? Or do you want the tables separated?
Platin  
```{r Table4 summary Platin}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

@@

@@

tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl9 <-
  tbl_merge(list(tbl6, tbl6))

tbl_stack(list(tbl7, tbl8, tbl9),
          group_header = c(
                           "carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery"),
          quiet = TRUE)
```
<br>

@@

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl9 <-
  tbl_merge(list(tbl6, tbl6))

tbl_stack(list(tbl7, tbl8, tbl9),
          group_header = c(
                           "paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo",
                           "paclitaxel Adj/Upfront Surgery"),
          quiet = TRUE)
```
<br>
<br>

@@

>>>>

Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ given}{expected\ dose}$$

@@

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.**

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
**But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.**

@@

study_criteria <- study_criteria %>%
  filter(!is.na(surgerydate)) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type))

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
```{r}
standard_care <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**

@@

```{r}
Frontline <- standard_care %>%
  filter(is.na(switch_drugs))
```

@@

# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

@@

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

### For Upfront Surgery
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

# Frontline <- 
#   full_join(Frontline, imputed_data %>% 
#               select(patientid, starts_with("imp_")), 
#             by = "patientid") 
Frontline <- 
  full_join(Frontline, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```

@@

```{r consort, fig.width=12}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("**Assessed for eligibility**") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

@@

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((
      therapy == "Upfront Chemo" &
        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
    ) | (
      therapy == "Upfront Surgery" &
        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
    )
    ),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)) %>% 
    filter(is.na(wrong_pacli_dosedense)) %>%
    filter(is.na(switch_drugs)),

    Frontline = standard_care,

  # anti_join is useful for counting exclusions -------------
    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    excluded1 = "excluded albeit flatiron recommendation",
    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
    flatiron_rec = "**Fit flatiron rec**",
    study_criteria = "**Fit study criteria**",
    missing_data = "**Non missing data**",
    Frontline = "**Population Study**"
  )

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • (Data from one PracticeID) <br>
      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include only patients who received platin and/or taxane <br>
      • exclude patients who only received neo + surgery <br>
      • include patients with single or dual P/T +/- Bev as frontline treatment
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

  consort_arrow_add(
    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
  ) %>%
  consort_arrow_add(
    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
```

@@

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

@@

@@

           histology1, "histology", "stagecat", imp_stagecat,

@@

<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
```{r Table 5}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat,
           "debulking", imp_debulking, "therapy"
           )) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```

<span style="color:green">**Table  Summary of the expected, actual dose, and RDI**</span>
```{r Summary of the expected, actual dose, and RDI}
rdi_study <- 
  RDI_data %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type))

tbl1 <- rdi_study %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>% 
  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type) %>% bold_labels()

tbl2 <- rdi_study %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>% 
  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type) %>% bold_labels()

tbl_stack(list(tbl1, tbl2),
          group_header = c(
                           "Carboplatin Upfront Chemo", 
                           "Paclitaxel Upfront Chemo"),
          quiet = TRUE)

tbl1 <- rdi_study %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>% 
  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity) %>% 
  tbl_summary() %>% bold_labels()

tbl2 <- rdi_study %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>% 
  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity) %>% 
  tbl_summary() %>% bold_labels()

tbl_stack(list(tbl1, tbl2),
          group_header = c(
                           "Carboplatin Upfront Surgery", 
                           "Paclitaxel Upfront Surgery"),
          quiet = TRUE)

# rdi_study %>% filter(drugname == "paclitaxel" & is_dose_dense == 1) %>% 
#   select(target_auc, expected_dose, amount,  relative_dose_intensity, therapy) %>% 
#   tbl_summary(by = therapy) %>% bold_labels()

```
<br>

@@

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_drug >= 0.85              ~ "adequate",
#     mean_RDI_per_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

@@

```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(y=raceeth, x=value,  fill=raceeth
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+
  geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+

@@

Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(y=bmi_cat, x=value,  fill=bmi_cat
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+
  geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+

@@

## 2.RDI summary table

@@

<span style="color:green">**Table 7: Summary RDI data by race and bmi**</span>  
Removing the overall on the right side? Or do you want the tables separated?
Platin  
```{r Table 7 Summary RDI data by race and bmi}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

@@

tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl_stack(list(tbl7, tbl8),
          group_header = c(
                           "carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo"),
          quiet = TRUE)

@@

# tbl9 <-
  tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Surgery**")
```
<br>

@@

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl_stack(list(tbl7, tbl8),
          group_header = c(
                           "paclitaxel Neo/Upfront Chemo", 
                           "paclitaxel Adj/Upfront Chemo"),
          quiet = TRUE)
tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Surgery**")
```
<br>
<br>

@@

```{r}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  mutate(comp_cases = case_when(
    is.na(stagecat) |
      is.na(debulking)                     ~ "excluded",
    TRUE                                   ~ "complete cases"
  )) %>% 
  select(c(vital, raceeth, 
           agecat, "ageatdx",

           histology1, "histology", "stagecat", imp_stagecat,

           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
           comp_cases)) %>% 
  tbl_summary(by = comp_cases) %>% 
  bold_labels() %>% add_p() %>% bold_p()
```
<br>
